Why there are more species in several small patches vs few large patches:

### 2024-11-11 ms_SLOSS.Rmd
Minor modifications add SI captions

![Relationship between the number of species and habitat patch size across panels representing different model versions and varying dispersal distances. The vertical panels correspond to different percentages of habitat destruction. In the neutral model, species are equivalent and share the same parameters; in the hierarchical model, species exhibit competitive dominance, with more dominant species replacing less dominant ones; and in the neutral with habitat selection model, species are neutral but propagules search for empty patches, ensuring survival. Simulations were performed using a fixed growth rate ($\lambda = 2$), with migration and replacement rates of 0.0001 and 0.3, respectively. After 600 time steps, the specified percentage of the habitat was destroyed, making it unavailable for species. The habitat destruction follows a regular pattern, with all patches being of equal size and uniformly spaced from one another.](Figures/AcrossBehav_MeanPatch_Species_Dispersal_Lambda2_pf_regular.png)

![Relationship between the number of species and habitat patch size across panels representing different model versions and varying dispersal distances. The vertical panels correspond to different percentages of habitat destruction. In the neutral model, species are equivalent and share the same parameters; in the hierarchical model, species exhibit competitive dominance, with more dominant species replacing less dominant ones; and in the neutral with habitat selection model, species are neutral but propagules search for empty patches, ensuring survival. Simulations were performed using a fixed growth rate ($\lambda = 2$), with migration and replacement rates of 0.0001 and 0.3, respectively. After 600 time steps, the specified percentage of the habitat was destroyed, making it unavailable for species. Habitat blocks of the same size (habitat patch size) were randomly distributed over the simulation grid. As a result, some patches overlapped, leading to a distribution of patch sizes.](Figures/AcrossBehav_MeanPatch_Species_Dispersal_Lambda2_pf_block.png)

>>>>

![Relationship between the number of species and habitat patch size across panels representing different model versions and varying dispersal distances under regular habitat destruction. The vertical panels correspond to different percentages of habitat destruction. In the neutral model, species are equivalent and share the same parameters; in the hierarchical model, species exhibit competitive dominance, with more dominant species replacing less dominant ones; and in the neutral with habitat selection model, species are neutral but propagules search for empty patches, ensuring survival. Simulations were performed using a fixed growth rate ($\lambda = 2$), with migration and replacement rates of 0.0001 and 0.3, respectively. After 600 time steps, the specified percentage of the habitat was destroyed, making it unavailable for species. The habitat destruction follows a regular pattern, with all patches being of equal size and uniformly spaced from one another.](Figures/AcrossBehav_MeanPatch_Species_Dispersal_Lambda2_pf_regular.png)

![Relationship between the number of species and habitat patch size across panels representing different model versions and varying dispersal distances ``````Ω¸under random block habitat destruction. The vertical panels correspond to different percentages of habitat destruction. In the neutral model, species are equivalent and share the same parameters; in the hierarchical model, species exhibit competitive dominance, with more dominant species replacing less dominant ones; and in the neutral with habitat selection model, species are neutral but propagules search for empty patches, ensuring survival. Simulations were performed using a fixed growth rate ($\lambda = 2$), with migration and replacement rates of 0.0001 and 0.3, respectively. After 600 time steps, the specified percentage of the habitat was destroyed, making it unavailable for species. Habitat blocks of the same size (habitat patch size) were randomly distributed over the simulation grid. As a result, some patches overlapped, leading to a distribution of patch sizes.](Figures/AcrossBehav_MeanPatch_Species_Dispersal_Lambda2_pf_block.png)
